Home

### 2020-04-16 analysis/index.Rmd
mr.ash description
veb-boost-repo

# References
  * VEB-boost
    * [Problem description](VEB-boost-fitting.html)
    * Andrew's [software](https://github.com/andrewg3311/VEB.Boost) and [workflowr website](https://andrewg3311.github.io/VEB-Boost-workflowR/VEB_Boost_Derivation.html)

>>>>

# References
  * VEB-boost
    * [Problem description](VEB-boost-fitting.html)
    * Andrew's [software](https://github.com/stephenslab/VEB.Boost) and [workflowr website](https://andrewg3311.github.io/VEB-Boost-workflowR/VEB_Boost_Derivation.html)

  * mr.ash
    * [mr.ash](https://github.com/stephenslab/mr.ash.alpha) package
    * [mr.ash workflowr website](https://stephenslab.github.io/mr-ash-workflow/)
